Multispecies survey for diet comp

### 2020-11-19 SurveyDietCompTest.Rmd
diet prop from survey, outline bias addition

@@

  # then apply id/aggregation bias--this adds prey categories that don't exist??

>>>>

    dat2 <- dat2 %>%
      group_by(species, agecl, time) %>%
      mutate(totcons = sum(sumcons)) %>%
      mutate(dietprop = sumcons/totcons) %>%
      arrange(species, agecl, time)

@@

  # then apply id/aggregation bias--this adds prey categories that don't exist??
  # user specified max proportion to reallocate
  # apply taxonomically, allocating fish prey to fish unid, invert prey to invert unid, then some portion unid
  # phytoplankton and zooplankton prey direct to unid?
